Appendix 1: sdmTMB statistical model description

### 2021-12-22 doc/appendix-model.Rmd
Cite VAST

* $\mathrm{Var}[y]$ to define the expected variance of the variable $y$, and

* a $^*$ superscript to represent interpolated or projected values as opposed to values at knot locations (e.g., $\omega$ vs. $\omega^*$).

@@

Spatiotemporal random fields are represented by $\boldsymbol{\epsilon}_t$ within sdmTMB. 
This has been chosen to match the representation in VAST (REF). 
The marginal standard deviation of $\boldsymbol{\epsilon}_t$ is indicated by `Spatiotemporal SD` in the model output or as `sigma_E` in the output of `sdmTMB::tidy(fit, "ran_pars")`.

>>>>

* $\mathrm{Var}[y]$ to define the expected variance of the variable $y$,

* a $^*$ superscript to represent interpolated or projected values as opposed to values at knot locations (e.g., $\boldsymbol{\omega}$ vs. $\boldsymbol{\omega}^*$), and

* where possible, notation has been chosen to match VAST [@thorson2019] to maintain consistency (e.g., $\boldsymbol{\omega}$ for spatial fields and $\boldsymbol{\epsilon}_t$ for spatiotemporal fields).

@@

Spatiotemporal random fields are represented by $\boldsymbol{\epsilon}_t$ within sdmTMB. 
This has been chosen to match the representation in VAST [@thorson2019]. 
The marginal standard deviation of $\boldsymbol{\epsilon}_t$ is indicated by `Spatiotemporal SD` in the model output or as `sigma_E` in the output of `sdmTMB::tidy(fit, "ran_pars")`.
